\bf What is the Best Way to Display Two Time Series to Read Association?

### 2016-02-01 paper/paper.Rnw
Citations

Reading correlation between two sets of non-temporal context numbers has been examined in many papers. In \citet{harrison2014ranking} different graphical displays of two sets of numbers are ranked of their effectiveness by Weber's Law \citep{webers} which provides a relationship between perception and the ``effect size'' in the data. For example, two series with correlation 0.9 should be proportionately easier to distinguish from noise than two series with correlation 0.3. The visual display should reflect this difference is ease. Early papers \citep{Cleveland1982,lane1985} showed that people read association from a scatterplot differently than they would linearly interpret a correlation coefficient.

>>>>

Reading correlation between two sets of non-temporal context numbers has been examined in many papers. In \citet{Harrison} different graphical displays of two sets of numbers are ranked of their effectiveness by Weber's Law \citep{webers} which provides a relationship between perception and the ``effect size'' in the data. For example, two series with correlation 0.9 should be proportionately easier to distinguish from noise than two series with correlation 0.3. The visual display should reflect this difference is ease. Early papers \citep{Cleveland1982,lane1985} showed that people read association from a scatterplot differently than they would linearly interpret a correlation coefficient.
